ZCB Pricing

### 2018-07-05 ZCB Pricing .Rmd
Added corrected bond function and some plots

bond_price <- function(alpha,beta,sigma,t,T,r){
  A <- (beta*(1-exp(-beta*(T-t))))/(alpha)
  B <- (1/beta)*((alpha-(sigma)^2/(2*beta))*(A - T +t) - (sigma^(2)*A^2)/(4))
  exp(-A*r +B)
}

@@

G <- CN(0.08,0.8,0.005,0.05,I=1:1000, J = seq(0,0.10,0.01))

>>>>

bond_price <- function(alpha,beta,sigma,t,T,r){
  A <- (1-exp(-beta*(T-t)))/(beta)
  B <- (1/beta)*((alpha-(sigma)^2/(2*beta))*(A - T +t) - (sigma^(2)*A^2)/(4))
  exp(-A*r +B)
}

@@

G <- CN(0.08,0.8,0.005,0.05,I=1:100, J = seq(-0.3,0.5,0.01))

#============================================================================================
# Doing some plots
plot(G)
xvec <- seq(-0.3,0.5,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
}
plot(G, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```
